Landscape composition and beneficial insects

### 2020-08-05 manuscript/manuscript_outline.Rmd
Got rid of old figure

Understanding of how landscape structure drives beneficial arthropod abundance is incomplete
Bees are generally driven by flower/nest substrate availability [@roulston2011]
Limited understanding of other arthropods (but see ``beetle hedges" from UK?)
Beetles are limited by water, food, and oviposition sites [@lovei1996]
No-till agriculture is better for some ground beetles [@busch_Msc]
Arachnids are similarly limited by food, shelter

Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
Spillover occurs when organisms migrate from suitable habitat patches
Can occur with pests or beneficial organisms [@woodcock2016]
Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance

Point estimates of abundance are influenced by spatio-temporal processes 
Arthropods move between landscape components depending on their life history
e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
This means that spillover depends not only on habitat type, but on time of the year
Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]

>>>>

Landscape structure drives beneficial arthropod abundance, and is key for understanding how to manage benefical insects
Bees are generally driven by flower/nest substrate availability [@roulston2011]
Limited understanding of other arthropods (but see ``beetle hedges" from UK?)
Beetles are limited by water, food, and oviposition sites [@lovei1996]
No-till agriculture is better for some ground beetles [@busch_Msc]
Arachnids are similarly limited by food, shelter

Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
Spillover occurs when organisms migrate from suitable habitat patches
Can occur with pests or beneficial organisms [@woodcock2016]
Contrast between landscape and local SNL is important [@boetzl2020; @vanSchalkwyk2020]; small patches can have a large effect if overall landscape lacks SNL
Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance

Abundance is also influenced by spatio-temporal processes, such as phenology and migration
Arthropods move between landscape components depending on their life history
e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
This means that spillover depends not only on habitat type, but on time of the year
Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
<!-- Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000] -->
